---
output:
  github_document:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```


## Overview

`"binomial"` is a minimal [R](http://www.r-project.org/) implementation for the statistical analysis of a simple binomial function.

* `bin_choose()` returns a value given t choose s
* `bin_distribution` returns a list given the probability of success given trials
* `plot.bindis()` plots the bin distribution
* `print.summary.binvar()` prints the summary based on a binomial variable


## Motivation

This package has been developed to describe some of the concepts
behind the creation of an R project, and to execute a basic concept such as binomials.


## Installation

Install the development version from GitHub via the package `"devtools"`:

```r
# development version from GitHub:
#install.packages("devtools") 
# install "cointoss" (without vignettes)
devtools::install_github("gastonstat/cointoss")
# install "cointoss" (with vignettes)
devtools::install_github("gastonstat/cointoss", build_vignettes = TRUE)
```


## Usage

```{r}
library(Binomial3)

# binchoose
bin_choose(6, 5)

# bin distrib/cumulative and plot
dis1 <- bin_distribution(trials = 5, prob = 0.5)
plot.bindis(dis1)


# summary and print
bin1 <- bin_variable(10, 0.3)
binsum1 <- summary.binvar(bin1)
print.summary.binvar(binsum1)

```
