---
title: "Binomial fun"
author: "Isaac Chap"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Binomial fun}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE)
library(Binomial3)
```


## Binomial

The package `"binomial"` is a minimal implementation for the statistical analysis of a simple binomial function.

## Creating private check functions

The first step is to create private check functions that checks if all the variables used 
in a binomial are valid values:

```{r check private funcs}
# check_prob
# check_trials
# check_success
```

They are private functions that are not meant to be called, but are used within the main functions and method functions.

Then, I created private aux functions that are also not meant to be called as a main function, but serves to be called by the main functions as well.

```{r aux private funcs}
# aux_mean
# aux_mode
# aux_variance 
```

## Main functions

Then I got into creating the main functions that are meant to be called by the user.

```{r binchoose}
bin_choose(6, 5)
bin_choose(4, 5)
```

bin_choose(6, 5) returns a nice value of 6 (6 choose 5), but bin_choose(4, 5) would print an error message.

## Plot

Eventually, through more functions the first part of the end results is plot.bindis and plot.bincum.
```{r plot with bindis bincum}
dis1 <- bin_distribution(trials = 5, prob = 0.5)
cum1 <- bin_cumulative(trials = 5, prob = 0.5)
plot.bindis(dis1)
plot.bincum(cum1)
```

bin_distribution and bin_cumulative displays a table of the results based on trials and probability, whereas plot.bindis/bincum can plot this dataframe into a nice graph.

## Summary

Final part is to create a summary utilizing all the private aux functions, then creating functions that prints it out nicely.

```{r printsummary}

bin1 <- bin_variable(10, 0.3)
print.binvar(bin1)

binsum1 <- summary.binvar(bin1)
print.summary.binvar(binsum1)
```

## Extra

Just incase you want to use individual functions to figure out mean, mode etc.
```{r bin other functions}

bin_mean(10, 0.4)
bin_variance(10, 0.4)
bin_mode(10, 0.4)
bin_skewness(10, 0.4)
bin_kurtosis(10, 0.4)
```
